---
title: Exploratory Data Analysis
format: typst
---

### Question 1

Which SR precinct with over 100 registered voters had the lowest proportion of registered voters who voted?

### Answer 1

``` {r}
sr_clean |>
    filter(TOTREG >= 100) |>
    mutate(prop = TOTVOTE/TOTREG) |>
    arrange((prop))
```

SR Precinct 060379001372A had only 254 voters out of 1866 total registered voters, with a proportion of .13612

### Question 2

Which SR precinct with at least 100 voters had the greatest proportion of voters for the democratic presidential candidate vs. the republican presidential candidate?

### Answer 2

``` {r}
sr_clean |>
    filter(TOTVOTE >= 100) |>
    mutate(prop = dem/rep) |>
    arrange(desc(prop))
```

SR Precinct 06001215110 had 2269 democratic votes to 61 republican votes, with a proportion of 37.19672

### Question 3

Were any SR precincts with at least 100 voters tied for democratic vs. republican presidential candidate?

### Answer 3

```{r}
sr_clean |>
    filter(TOTVOTE >= 100) |>
    filter(dem == rep)
```

Yes, there were actually 38 precincts that were tied for republican and democratic votes.